---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# horus

**WIP -- Very early build, things are very likely to change -- WIP**

The goal of horus is to allow quick visualization methods for common machine learning and modeling tasks. This project is hugely inspired by the Python library [yellowbrick](https://github.com/DistrictDataLabs/yellowbrick).

## Installation

For the time being `horus` is only available on Github, and can be installed
with `devtools`:

```{r, eval=FALSE}
# install.packages('devtools')
devtools::install_github('EmilHvitfeldt/horus')
```

In the future the package will be available on CRAN as well.

## Example

There is no reason why a principal component plot of a dataset should be as hard as it corrently is in R. Using **horus** it is down to a single line!

```{r}
library(horus)
viz_pca(iris, Species)
```

